---
title: "Introduction to the CCC package"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package implements the "3C-strategy": Categorization, Clustering, Classification that had been developed for application in medical research, specifically , to refine a diagnosed diseases to more relevant classes.

## C1 - Categorization

The analysis in the package assumes that the data has be prepoccessed as follows: highly correlated variables removed, missing values handled and varialbes were transformed for symmetry.

In the first step, features are categorized, according to experts knowledge, to three categories:
  + __Clinical Measures (CM)__ - Disease symptoms, Patients' functional state and abilities.  
  + __Potential Biomarkers (PB)__ - Imaging, Proteins, Genetics etc.  
  + __Assigned Diagnosis (DX)__ - The patients' diagnoses.   
  
Each feature category is registered in an auxilary file, which includes to columns:
One named "varName", which is the variable/column name from the data file, and another column named "varCategory" which is the categorization of the variable (i.e.: Dx, CM or PB from the categorization done in stage C1).     
  
A second file includes the data itself: data with Dx (disease diagnosis), CM (Clinical
measurements) PB (Potential biomarkers). Each row indicates a patient.   

```{r, message=FALSE, warning=FALSE, tidy=TRUE}
data(c3_sample2)
data(c3_sample2_categories)
head(c3_sample2_categories) 
table(c3_sample2_categories[,"varCategory"])
head(c3_sample2)[, 1:5]
```

## C2 - Clustering

This step includes:
1. __Feature Selection__: The initial screening of clinical features using the assigned diagnosis as target.  
2. __decision for number of clusters__: The selected features are used to decide the appropriate number of clusters, using K-gap statistic.
3. __Clustering__

```{r, message=FALSE, warning=FALSE, tidy=TRUE}
library(CCC)  
CM_AD_matrix <- get_xy_from_DATA_C2(c3_sample2, c3_sample2_categories)
  x <- CM_AD_matrix[[1]]  # CM matrix
  y <- CM_AD_matrix[[2]]  # DD vector
  
  C2_results <- C2(x[,1:50] , y, feature_selection_method="RF", num_clusters_method="Manhattan", clustering_method="Manhattan", plot.num.clus=TRUE, plot.clustering=TRUE, k=6)

C2_results
```

When k is missing, the K-gap statistic plot and summary are presented and teh user may choose the value.

## C3 - Classification
  
1. __Potential Biomarkers selection__ (supervised)  
Using our newly assigned clusters from C2 we try to identify potential biomarkers using the newly created clusters as the target.  
Same algorithms as for stage C2. 

2. __Clusters biomarkers classification__ (supervised)  

Running the C3 function:  
Finally, we will create a new response variable (named "newy") using the assigned diagnoses obtained in step C2.  
We will also create a data frame that consists of PB variables from our initial data file.  
We will use both of the above to create a new classification based on the PB variables.  

Feature Selection method: Random Forest (Default)   
Classification: Random Forest (Default)
      
        
```{r, message=FALSE, warning=FALSE, tidy=TRUE}
# Creating PB matrix
PBx <- get_PBx_from_DATA_C3(c3_sample2, c3_sample2_categories)
newy <- unlist(C2_results[[3]])
C3_results <- C3(PBx, newy, feature_selection_method="RF", classification_method="RF") 
C3_results
table(newy, C3_results[[2]])
```
  
